NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-29 aaV_main.tex
few mods
updates
updates to results
draft of aaa results section adaption of aaw diagrams to e- production
update xs table
update draft, added abstract and conclusions

%\textwidth=20cm
%\textheight=16cm
%\setlength{\oddsidemargin}{-1cm}
\pdfoutput=1
\setlength\parindent{0pt}

@@

%%% Macros
\newcommand{\eqn}[1]{Eq.~(\ref{#1})}
\newcommand{\ab}{\ensuremath{\alpha_0}}
\newcommand{\als}{\ensuremath{\alpha_s}}
\newcommand{\aapa}{\ensuremath{\gamma\gamma}}
\newcommand{\shortequal}{\ensuremath{\!\!\!=\!\!\!}}
\newcommand{\pT}{\ensuremath{p_\text{T}}}
\newcommand{\order}{\ensuremath{\mathcal{O}}}

@@

@@

\abstract{
  We calculate the next-to-leading order electroweak corrections...
}

>>>>

%\textwidth=20cm
%\textheight=16cm
%\setlength{\oddsidemargin}{-1cm}
\pdfoutput=1
% \setlength\parindent{0pt}

@@

\newlength{\unitcharwidth}
\settowidth{\unitcharwidth}{1}

\newlength{\unitsuperscriptwidth}
\settowidth{\unitsuperscriptwidth}{\scriptsize 1}

%%% Macros
\newcommand{\rd}{\ensuremath{\mathrm{d}}}
\newcommand{\eqn}[1]{Eq.~(\ref{#1})}
\newcommand{\Gmu}{\ensuremath{G_\mu}}
\newcommand{\alphazero}{\ensuremath{\alpha(0)}}
\newcommand{\alphaGmu}{\ensuremath{\alpha_{\Gmu}}}
\newcommand{\alphas}{\ensuremath{\alpha_s}}
\newcommand{\aaa}{\ensuremath{\gamma\gamma\gamma}}
\newcommand{\aaw}{\ensuremath{\gamma\gamma W}}
\newcommand{\aaz}{\ensuremath{\gamma\gamma Z}}
\newcommand{\shortequal}{\ensuremath{\!\!\!=\!\!\!}}
\newcommand{\pT}{\ensuremath{p_\text{T}}}
\newcommand{\pTveto}{\ensuremath{p_\text{T,jet}^\text{veto}}}
\newcommand{\order}{\ensuremath{\mathcal{O}}}
\newcommand{\vP}{\ensuremath{\vphantom{\int_a^b}}}

@@

\newcommand{\QCDpEW}{QCD+EW}
\newcommand{\QCDtEW}{QCD$\times$EW}
\newcommand{\deltaQCD}{\ensuremath{\delta_\text{QCD}}}
\newcommand{\deltaEW}{\ensuremath{\delta_\text{EW}}}
\newcommand{\muR}{\ensuremath{\mu_{\mathrm{R}}}}
\newcommand{\muF}{\ensuremath{\mu_{\mathrm{F}}}}

@@

\abstract{
Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
couplings. They allow for a constraint of anomalous gauge couplings, where new physics might predominantly
couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
 in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
 when combining
QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
}

### 2017-10-29 conclusions.tex
update draft, added abstract and conclusions

\section{Conclusions}
\label{sec:conclusions}

We did good.

>>>>

\section{Conclusions}
\label{sec:conclusions}
Processes that involve vertices of three and four electroweak gauge bosons are among the most promising processes
where new physics might be found. Deviations from the Standard Model couplings or vertices that do not exist in the 
Standard Model might be found. The deviations from the Standard Model predictions can for instance conveniently 
described by higher dimensional operators in terms of an effective field theory. Precise measurements of these  
processes allow to constrain and set limits to these higher dimensional operators.\\
In this paper we investigated the Standard Model predictions to a subset of such processes where we require
two photons plus an additional electroweak vector boson in the final state.  As additional vector boson we allowed
for a third photon a well as for a $W$ or $Z$ boson where we considered the leptonic decay of the heavy bosons.
This particularly implies that all non-resonant contributions are taken into account as well.\\
We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of fiducial cuts. Particular
emphasize has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to a few per cent for the $\gamma\gamma l^{+}l^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

### 2017-10-29 results.tex
implement alpha(0) for NLO EW
update draft, added abstract and conclusions

In this section we present numerical results for the NLO QCD and NLO EW 
corrections to all three production processes of a diphoton pair in 
association with a third vector boson, a third photon, a $W$ or a $Z$ 
boson, at the LHC at a centre-of-mass energy of 13\,TeV. 
In case of an accompanying $W$ or a $Z$ boson, we consider the full 
off-shell leptonic final state, i.e.\ lepton-neutrino or lepton-pair 
production.
All results are obtained in the Standard Model using the complex-mass 
scheme \cite{Denner:2005fg} with the following input parameters
\begin{center}
  \begin{tabular}{rclrcl}
    $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
    $\Gmu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
    $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
    $m_t$ &\shortequal& $173.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
  \end{tabular}
\end{center}
While we calculate triple photon production in the \alphazero-scheme, 
we use a mixed scheme for \aaw\ and \aaz production: at LO two 
powers of $\alpha$ are taken in the \alphazero-scheme, while 
one power of $\alpha$ is taken in the \Gmu-scheme. 
The additional power of $\alpha$ in the NLO EW correction 
is evaluated in \alphazero-scheme again.
The virtual amplitudes are renormalised correspondingly.
In all cases both the width of the top quark and the Higgs boson 
can safely be neglected as there are no diagrams containing either 
as $s$-channel propagators which can potentially go on-shell. 
All other lepton and parton masses and widths are set to zero, 
i.e.\ we are working in the five-flavour scheme.
We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
\cite{}. 
The use of a QCD-only PDF is justified by the fact that, 
at LO, the photon induced corrections are either non-existant 
(\aaa, \aaw) or negligible (\aaz).
This finding will be detailed in Section \ref{sec:results:aaz}.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  \begin{split}
    \muR^0 = \muF^0 = \left\{
    \begin{array}{ll}
      m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' & \text{in \aaw\ and \aaz\ production.}
    \end{array}\right.
  \end{split}
\end{equation}
Therein, the modified scalar sum of transverse momenta is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively.
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
and $-4.6\%$ (\aaz).

@@

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recoveren, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses. 
Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
the electroweak corrections are again not covered by the LO 
uncertainty estimate.

@@

Next we move on to diphoton production in association with 
a $W$ boson decaying leptonically.
In this context, we will representatively focus on $W^-$ bosons 
as we do not expect qualitatively different results for $W^+$ 
bosons. 
We define our fiducial phase space by the following. 
First, we require the presence of exactly one charged lepton, 
dressed with all photons in a cone of size $R=0.1$, with 
$\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Among the remaining photons we require at least two identified 
ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
only changing the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
We put no requirements on the missing transverse momentum. 
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.
\comment{MS: Nico, please check!}

@@

Figure \ref{fig:aaw:pt} shows the transverse momenta of 
the leading and subleading photon as well as the charged 
lepton. 
As was observed in tiple photon production, the inclusive 
NLO QCD corrections are large. 
Nonetheless, they differ substatially between the three 
oberservables and in their different regions. 
While $\deltaQCD$ rises from values of 0.3 at small 
transverse momenta of the leading photon to 2 at 
$\pT\approx 100\,\text{GeV}$, it remains constant above that 
value.
In the subleading photon's transverse momentum, the 
situation is different. 
Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
at 500\,GeV. 
The behaviour of the QCD corrections to the lepton \pT are 
then again qualitatively similar to that of the leading 
photon, start at $\deltaQCD=0.8$ at low \pT and rising 
steeply to 2.5 at 100\,GeV and then gradually leveling out 
at 3.5. 
Again, the presence of a restrictive jet veto has little 
effect on the small transverse momentum regions, but 
effectively contains the size of the NLO QCD corrections 
to remain below $\deltaQCD=0.5$. 
Instead, they are again driven negative, reaching 
$-20-30\%$ for all three observables.

The electroweak corrections are negative throughout, 
reaching $-20\%$ for the leading photon and the lepton 
and $-20\%$ for the subleading photon at 500\,GeV. 
For this process, starting at transverse momenta of 
around 100\,GeV, the electroweak corrections are much 
larger than the LO uncertainty estimate.
Due to their larger size, as compared with the \aaa\ 
production process, the difference between their 
additive and multiplicative combination with the 
QCD corrections becomes more pronounced when no 
jet veto is applied. 
One reason is that the QCD corrections are dominated 
by real emission contributions, which only receive the 
not-so-small electroweak correction factor in the 
multiplicative combination, but not the additive one. 
While this correction factor is, strictly speaking, 
associated only with the Born configuration, its 
application to real-emission configurations is well 
motivated in the electroweak Sudakov-regime at 
large transverse momenta. 
The concurrence of the additive and multiplicative 
schemes in the presence of the jet veto now precisely 
originates in the taming of the QCD corrections by 
restricting the influence of real-emission topologies.

@@

Figure \ref{fig:aaa:myy} also displays the transverse 
mass of the $W$ boson on the right hand side. 
This distribution exhibits the general features known 
from inclusive $W$ production, only the QCD corrections 
are scaled to the values present in this process.
Electroweak corrections are less pronounced than for 
the invariant masses, but are still non-negligible. 
They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
and $-14\%$ at 1\,TeV.

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
again loosening the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
We put no requirements on the missing transverse momentum. 
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.
\comment{MS: Nico, please check!}

@@

In close analogy with the previous two processes considered, 
we start our discussion of the results with the transverse 
momenta of the leading and subleading photon and the charged 
lepton pair, cf.\ Figure \ref{fig:aaz:pt}. 
The first observation is, while the general behaviour of the 
spectra is the same as in \aaw production, the inclusive QCD 
corrections are much smaller in this case. 
They range between $\deltaQCD=0.3-0.4$ for the leading and 
subleading photon and rise to 0.7 for the lepton pair at 
500\,GeV. 
The restrictive jet veto employed for the previous process 
reduces the QCD corrections further. 
Beyond the negligible impact at very small transverse 
momenta, they turn negative early on, reaching $\deltaQCD=-0.2-0.4$ 
at 500\,GeV. 
The electroweak corrections negative throughout, increasing 
from $\deltaEW=-5\%$ at low transverse momenta to $-20\%$ at 
500\,GeV.
They are consistently larger than the LO uncertainty estimate. 
As a consequence, the difference between the additive and 
multiplicative is comparably large, especially in the high 
\pT regions.

>>>>

In this section we present numerical results for the NLO QCD and NLO EW 
corrections to all three production processes of a diphoton pair in 
association with a third vector boson, a third photon, a $W$ or a $Z$ 
boson, at the LHC at a centre-of-mass energy of 13\,TeV. 
In case of an accompanying $W$ or a $Z$ boson, we consider the full 
off-shell leptonic final state, i.e.\ lepton-neutrino or lepton-pair 
production.
All results are obtained in the Standard Model using the complex-mass 
scheme \cite{Denner:2005fg} with the following input parameters
\begin{center}
  \begin{tabular}{rclrcl}
    $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
    $\Gmu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
    $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
    $m_t$ &\shortequal& $173.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
  \end{tabular}
\end{center}
While we calculate triple photon production in the \alphazero-scheme, 
we use a mixed scheme for \aaw\ and \aaz production: at LO two 
powers of $\alpha$ are taken in the \alphazero-scheme, while 
one power of $\alpha$ is taken in the \Gmu-scheme. 
The additional power of $\alpha$ in the NLO EW correction 
is evaluated in \alphazero-scheme again.
The virtual amplitudes are renormalised correspondingly.
In all cases both the width of the top quark and the Higgs boson 
can safely be neglected as there are no diagrams containing either 
as $s$-channel propagators which can potentially go on-shell. 
All other lepton and parton masses and widths are set to zero, 
i.e.\ we are working in the five-flavour scheme.
We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
\cite{Dulat:2015mca}, interfaced through LHAPDF6 \cite{Buckley:2014ana}. 
The use of a QCD-only PDF is justified by the fact that, 
at LO, the photon induced corrections are either non-existant 
(\aaa, \aaw) or negligible (\aaz).
This finding will be detailed in Section \ref{sec:results:aaz}.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  %\begin{split}
    \muR^0 = \muF^0 = %\left\{
    %\begin{array}{ll}
     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
    %\end{array}\right.
  %\end{split}
\end{equation}
In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
transverse momenta, for the two processes with the massive vector bosons it is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{Berger:2009ep}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively.
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
and $-4.4\%$ (\aaz).

@@

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recovered, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses. 
Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
the electroweak corrections are again not covered by the LO 
uncertainty estimate.

@@

Next we move on to diphoton production in association with 
a $W$ boson decaying leptonically.
In this context, we will representatively focus on $W^-$ bosons 
as we do not expect qualitatively different results for $W^+$ 
bosons. 
We define our fiducial phase space by the following. 
First, we require the presence of exactly one charged lepton, 
dressed with all photons in a cone of size $R=0.1$, with 
$\pT>20\,\text{GeV}$ and $|\eta|<2.5$. 
Among the remaining photons we require at least two identified 
ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
only changing the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.7$.
Furthermore we require the transverse mass of the lepton-neutrino system
to be larger than $40\, \text{GeV}$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

Figure \ref{fig:aaw:pt} shows the transverse momenta of 
the leading and subleading photon as well as the charged 
lepton. 
As was observed in triple photon production, the inclusive 
NLO QCD corrections are large. 
Nonetheless, they differ substatially between the three 
oberservables and in their different regions. 
While $\deltaQCD$ rises from values of 0.3 at small 
transverse momenta of the leading photon to 2 at 
$\pT\approx 100\,\text{GeV}$, it remains constant above that 
value.
In the subleading photon's transverse momentum, the 
situation is different. 
Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
at 500\,GeV. 
The behaviour of the QCD corrections to the lepton \pT are 
then again qualitatively similar to that of the leading 
photon, start at $\deltaQCD=0.8$ at low \pT \, and rising 
steeply to 2.5 at 100\,GeV and then gradually leveling out 
at 3.5. 
Again, the presence of a restrictive jet veto has little 
effect on the small transverse momentum regions, but 
effectively contains the size of the NLO QCD corrections 
to remain below $\deltaQCD=0.5$. 
Instead, they are again driven negative, reaching 
$-20-30\%$ for all three observables.

The electroweak corrections are negative throughout, 
reaching $-20\%$ for the leading photon and the lepton 
and $-25\%$ for the subleading photon at 500\,GeV. 
For this process, starting at transverse momenta of 
around 100\,GeV, the electroweak corrections are much 
larger than the LO uncertainty estimate.
Due to their larger size, as compared with the \aaa\ 
production process, the difference between their 
additive and multiplicative combination with the 
QCD corrections becomes more pronounced when no 
jet veto is applied. 
One reason is that the QCD corrections are dominated 
by real emission contributions, which only receive the 
not-so-small electroweak correction factor in the 
multiplicative combination, but not the additive one. 
While this correction factor is, strictly speaking, 
associated only with the Born configuration, its 
application to real-emission configurations is well 
motivated in the electroweak Sudakov-regime at 
large transverse momenta. 
The concurrence of the additive and multiplicative 
schemes in the presence of the jet veto now precisely 
originates in the taming of the QCD corrections by 
restricting the influence of real-emission topologies.

@@

Figure \ref{fig:aaw:myy} also displays the transverse 
mass of the $W$ boson on the right hand side. 
This distribution exhibits the general features known 
from inclusive $W$ production, only the QCD corrections 
are scaled to the values present in this process.
Electroweak corrections are less pronounced than for 
the invariant masses, but are still non-negligible. 
They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
and $-14\%$ at 1\,TeV.

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
loosening the transverse momentum requirements to 
$\pT>15\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

In close analogy with the previous two processes considered, 
we start our discussion of the results with the transverse 
momenta of the leading and subleading photon and the charged 
lepton pair, cf.\ Figure \ref{fig:aaz:pt}. 
The first observation is, while the general behaviour of the 
spectra is the same as in \aaw production, the inclusive QCD 
corrections are much smaller in this case. 
They range between $\deltaQCD=0.3-0.4$ for the leading and 
subleading photon and rise to 0.7 for the lepton pair at 
500\,GeV. 
The restrictive jet veto employed for the previous process 
reduces the QCD corrections further. 
Beyond the negligible impact at very small transverse 
momenta, they turn negative early on, reaching $\deltaQCD=-0.2-0.4$ 
at 500\,GeV. 
The electroweak corrections are negative throughout, increasing 
from $\deltaEW=-4\%$ at low transverse momenta to $-20\%$ at 
500\,GeV.
They are consistently larger than the LO uncertainty estimate. 
As a consequence, the difference between the additive and 
multiplicative is comparably large, especially in the high 
\pT\ regions.

### 2017-10-29 setup.tex
update draft, added abstract and conclusions

This combination of tools was previously used to calculate the 
NLO QCD corrections to \ldots \cite{} and the 
NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.

>>>>

This combination of tools was previously used to calculate the 
NLO QCD corrections to $ZZ+j$, $h+0,1,2,3\,\text{jets}$ , $W^{+}W^{-}b\bar{b}$ production 
\cite{Binoth:2009wk,Hoeche:2013mua,Greiner:2015jha,Greiner:2016awe,Heinrich:2013qaa,Heinrich:2017bqp} and the 
NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.
